Reducing RES Droughts through the integration of wind and PV

### 2025-01-15 Article2/elsarticle-template-harv.tex
Add info for title page

\author[Math]{Boris Morin} %% Author name
\author[Math]{Aina Maimo Far} %% Author name
\author[Eng]{Damian Flynn} %% Author name
\author[Math]{Conor Sweeney} %% Author name

%% Author affiliation
\affiliation[Math]{organization={University College Dublin, School of Mathematics and Statistics}, %Department and Organization
            addressline={}, 
            city={Dublin},
            postcode={}, 
            country={Ireland}}

\affiliation[Eng]{organization={University College Dublin, School of Electrical and Electronic Engineering}, %Department and Organization
        	addressline={}, 
        	city={Dublin},
        	postcode={}, 
        	country={Ireland}}

>>>>

\author[Math]{Boris Morin \corref{cor1}} %% Author name
\ead{boris.morin@ucdconnect.ie}

\author[Math]{Aina Maimo Far} %% Author name
\ead{aina.maimofar@ucd.ie}

\author[Eng]{Damian Flynn} %% Author name
\ead{damian.flynn@ucd.ie}

\author[Math]{Conor Sweeney} %% Author name
\ead{conor.sweeney@ucd.ie}

%% Author affiliation
\affiliation[Math]{organization={School of Mathematics and Statistics, University College Dublin}, %Department and Organization
	addressline={Belfied, Dublin 4}, 
	city={Dublin},
	postcode={D04 V1W8}, 
	country={Ireland}}

\affiliation[Eng]{organization={School of Electrical and Electronic Engineering, University College Dublin}, %Department and Organization
	addressline={Belfied, Dublin 4}, 
	city={Dublin},
	postcode={D04 V1W8}, 
	country={Ireland}}

\cortext[cor1]{Correponding author}
